---
title: 'To: Professor Green'
author: 'from: Dewi Djajaatmadja & Zeyang Wu'
date: "May 13, 2017"
output:
  pdf_document: default
---

#### RE: Aiding Africa Project
```{r eval=FALSE, include=FALSE}
# Course: BUAN 5260
# Title: Midterm Project
# Purpose: Midterm
# Date: May 11, 2018
# Author: Dewi Djajaatmadja, Zeyang Wu
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Clear packages 
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(
  paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
  detach, character.only = TRUE, unload = TRUE)

# Clear environment
rm(list = ls(all = TRUE)) 

```

```{r include=FALSE}
#load the packages
library(dplyr)
library(igraph)
library(lpSolveAPI)

# Read source file
s <- read.csv('5260_S18_Aiding_Africa_Data.csv', as.is = T, skip = 1)[1:30,]

 # Capture speed and capacity for each transit mode
t1 <- `colnames<-`(s[1:3, 1:3], c('mode', 'cap', 'speed'))
  
# Capture transit mode, distance, and cost for each route
t2 <- `colnames<-`(s[, 8:12], c('from', 'to', 'mode', 'dist', 'cost'))

values <- c('Airplane', 'Ship', 'Truck')
index <- c('400', '35', '50')
t2$speed <- as.numeric(index[match(t2$mode, values)])


values <-c('New York, NY','Jacksonville, FL','Lusaka, Zambia','Libreville, Gabon','Nairobi, Kenya','Khartoum, Sudan','Luanda, Angola','Dakar, Senegal','Niamey, Niger','Kosongo, D.R. Congo','Ndjamena, Chad')
index <- c('1', '2','3','4','5','6','7','8','9','10','11')

t2$form1 <- as.numeric(index[match(t2$from, values)])
t2$to1 <- as.numeric(index[match(t2$to, values)])

t2$time <- t2$dist/t2$speed #create time column
t2$time=round(t2$time,2) #round the time to 2 digits
```

## Network graph
For the Aiding Africa problem, it consists 11 cities, 2 origins from the US and 9 destinations in the Africa. 6 of the Africa cities are used as connections to the other 3. The 11 cities are linked by 30 routes, every route is conducted by 1 of the 3 transportation modes(airplane, ship, truck). For each route, it has unique cost and vehicle capacities. The graph below shows the relationship between the cities and the routes. 

```{r echo=FALSE, fig.height= 6}

# import data file
seer <-  t2[, 7:9]

# Make graph by setting 11 nodes/vertices, edges from nodes/vertices and distances from data matrix
g <- add_edges(make_empty_graph(n = 11, directed = FALSE), 
               t(seer[, 1:2]), weight=seer[,3]) %>%
# Set vertice/node names 
  set_vertex_attr("name", value = c("NY","FL","Senegal","Gabon","Angola","Sudan","Zambia","Kenya", "Niger", "Congo", "Chad"))

# Set coordinates so looks similar to book diagram
  ## This is just for visualization, but could include it in data file
 g$layout <- matrix(c(0,   0,  100,  100,  100, 100,  100, 100,  200, 200,  200, 
                     160, 130, 180, 165, 150, 135, 120, 105, 170, 145, 120), nc = 2)

# Lable edges with the distance or weight
#E(g)$label <- seer[, 3]

# Show network graph
graph<- plot(g, vertex.size=37, vertex.color="plum3", vertex.label.color="white")

```


## Case 1 - Shortest Paths
The minimine travel time among the 11 cities takes 592.44 hours to complete. For the shortest paths, Table 1 shows the quickest travel routes and time needed from the 2 cities in the US to the 9 destinations in Africa. 

The route that indicate significant time bottlenecks is from "Jacksonville, Florida" to "Lusaka, Zambia", this route needs to reduce 0.68 hours (approximately 41 minutes) to affect vehicle allocation across the netwoek and decrease the minumum total travel time. 

```{r include=FALSE}
# Set up model
sr <- make.lp(0, 31)

# 20.25, 172.11, 20.13, 17.60, 186.46, 119.20, 19.86, 180.83, 19.90, 17.71, 195.09, 112.11, 10.18, 20.64, 6.31, 5.16, 58.32, 33.12

# Set objective fn and constraints
obj_fn <- c(0, as.vector(t2$time))
set.objfn(sr, obj_fn)

add.constraint(sr, c( 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 9) #1
add.constraint(sr, c( -1, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 0) #2
add.constraint(sr, c( 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0), "=", -1) #3
add.constraint(sr, c( 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0), "=", -1) #4
add.constraint(sr, c( 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0), "=", -1) #5
add.constraint(sr, c( 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0), "=", -1) #6
add.constraint(sr, c( 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0), "=", -1) #7
add.constraint(sr, c( 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1), "=", -1) #8
add.constraint(sr, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, -1, -1, -1, -1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -1) #9
add.constraint(sr, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, -1, -1, -1, -1, -1, 0, 0, 0, 0, 0, 0), "=", -1) #10
add.constraint(sr, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, -1, -1, -1, -1, -1), "=", -1) #11

 dimnames(sr) <- list(c("NY", "FL", "Zambia", "Gabon", "Kenya", "Sudan", "Angola", "Senegal", "Niger", "Congo", "Chad"), c("Dummy", "NY-ZM","NY-GA","NY-KE","NY-SU","NY-AN","NY-SE","FL-ZM","FL-GA","FL-KE","FL-SU","FL-AN","FL-SE","ZM-NI","GA-NI","KE-NI","SU-NI","AN-NI","SE-NI","ZM-CO","GA-CO","KE-CO","SU-CO","AN-CO","SE-CO","ZM-CH","GA-CH","KE-CH","SU-CH","AN-CH","SE-CH"))
 
 # Solve the model
solve(sr)

# Make results and sensitivity table 
ps <- get.primal.solution(sr)
obj_sa <- get.sensitivity.obj(sr)
rhs_sa <- get.sensitivity.rhs(sr)

nv <- length(get.variables(sr))
mc <- length(get.constr.type(sr))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)], 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(sr), colnames(sr))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Objective value and sensitivity analysis table
ov
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)
as.table(sa_tab)
```

\begin{table}
\caption{Shortest travel time(For Case 1)}
\centering
\begin{tabular}[t]{l l r r}
\hline
\textbf{Departure City} & \textbf{Arrival City} & \textbf{Travel Time (hr)} & \\
\hline
New York, NY & Libreville, Gabon & 172.11\\

New York, NY & Khartoum, Sudan & 17.6\\

New York, NY & Luanda, Angola & 186.46\\

Jacksonville, Florida & Lusaka, Zambia & 19.86\\

Jacksonville, Florida & Nairobi, Kenya & 19.9\\

Jacksonville, Florida & Khartoum, Sudan & 112.11\\

New York, NY(Through Khartoum, Sudan) & Niamey, Niger &  22.76\\

New York, NY(Through Khartoum, Sudan) & Kosongo, D.R. Congo  &  21.04\\

New York, NY(Through Khartoum, Sudan) & Ndjamena, Chad  &  20.60\\
\hline
Total &  & 592.44\\

\end{tabular}
\end{table}


\pagebreak


## Case 2 - Minimum cost flow

Network path that minimize total cost incurs a total expense of $310,861,299 USD. This value is an underestimate as it allocates number of vehicles to its decimals, which might not be realistic. So to achieve the minimum cargo requirement of each city, should round-up the number of vehicles to nearest integer.

In this case, some restictions were applied: Niamey, Niger, can only recieve cargo via air; Ndjamena, Chad, cannot receive more than 840 trucks from each port; routes between Lusaka, Zambia to Ndjamena, Chad, and Khartoum, Sudan to Ndjamena, Chad can only allow 200 flights from each airfield.  Despite these restrictions, the cargo needs of all 9 destinations are still fully satisfied. Table 2 lists the routes used to achieve the minimum cost path, and the vehicle allocations for each of these routes.

There are three routes tied for tighest bottleneck: Jacksonville, FL to Lusaka, Zambia; New York, NY to Nairobi, Kenya; and Luanda, Angola, to Kosongo, D.R. Congo. The route from Jacksonville, FL to Lusaka, Zambia needs to reduce costs by at most $1,000 USD to decrease the minimum total transit cost.


```{r include=FALSE}
# Set really high cost M
M <- 999*1000

# Set up model
mcf <- make.lp(0, 30)

# Set objective fn
obj_fn <- c(32000,	30000,	30000,	45000,	50000,	55000,	56000,	48000,	44000,	49000,	57000,	61000,	M,5000,	9000,	M,	4000,	7000,	M,	5000,	8000,	22000,	19000,	4000,	24000,	22000,	23000,	28000,	25000,	2000)
set.objfn(mcf, obj_fn)

# Set Constraints
add.constraint(mcf, c(240,240,240,150,150,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "<=",  500000) #NY
add.constraint(mcf, c(0,0,0,0,0,0,240,240,240,150,150,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "<=",  500000) #FL
add.constraint(mcf, c(-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,17.7,17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "<=",  -50000) #Senegal
add.constraint(mcf, c(0,-240,0,0,0,0,0,-240,0,0,0,0,0,0,0,17.7,17.7,17.7,0,0,0,0,0,0,0,0,0,0,0,0), "<=",  -100000) #Gabon
add.constraint(mcf, c(0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,0,0,0,0,17.7,17.7,17.7,0,0,0,0,0,0,0,0,0), "<=",  -130000) #Angola
add.constraint(mcf, c(0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,0,0,0,0,0,0,150,150,150,0,0,0,0,0,0), "<=",  -90000) #Sudan
add.constraint(mcf, c(0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,0,0,0,0,0,0,0,0,150,150,150,0,0,0), "<=",  -150000) #Zambia
add.constraint(mcf, c(0,0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,150,150), "<=",  -120000) #Kenya
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,-17.7,0,0,-17.7,0,0,-17.7,0,0,-150,0,0,-150,0,0,-150,0,0), "<=",  -100000) #Niger
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,-17.7,0,0,-17.7,0,0,-17.7,0,0,-150,0,0,-150,0,0,-150,0), "<=",  -180000) #Congo
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-17.7,0,0,-17.7,0,0,-17.7,0,0,-150,0,0,-150,0,0,-150), "<=",  -80000) #Chad

# other constraints
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "<=", 840*17.7) #SeCh
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0,0,0), "<=", 840*17.7) #GaCh
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0), "<=", 840*17.7) #AnCh
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0), "<=", 200*150) #SuCh
add.constraint(mcf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0), "<=", 200*150) #ZaCh

dimnames(mcf) <- list(c("NY", "FL","Senegal", "Gabon", "Angola",
                       "Sudan", "Zambia", "Kenya", "Niger", "Congo", "Chad", 
                       "Senegal-Chad Truck Limit","Gabon-Chad Truck Limit", "Angola-Chad Truck Limit", "Sudan-Chad Flight Limit", 
                       "Zambia-Chad Flight Limit"),
                       c("NySe",	"NyGa",	"NyAn",	"NySu",	"NyZa",	"NyKe",	"FlSe",	"FlGa",	"FlAn",	"FlSu",	"FlZa",	"FlKe",	"SeNi",	"SeCo",	"SeCh",	"GaNi",	"GaCo",	"GaCh",	"AnNi",	"AnCo",	"AnCh",	"SuNi",	"SuCo",	"SuCh",	"ZaNi",	"ZaCo",	"ZaCh",	"KeNi",	"KeCo",	"KeCh") )
	
# Solve the model
solve(mcf)

# Make results and sensitivity table 
ps <- get.primal.solution(mcf)
obj_sa <- get.sensitivity.obj(mcf)
rhs_sa <- get.sensitivity.rhs(mcf)

nv <- length(get.variables(mcf))
mc <- length(get.constr.type(mcf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)], 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mcf), colnames(mcf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Objective value and sensitivity analysis table
ov
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)
as.table(sa_tab)
```

\begin{table}
\caption{Recommended Routes for Minimum Cost Allocation(For case 2)}
\centering
\begin{tabular}[t]{l l r r}
\hline
\textbf{Departure City} & \textbf{Arrival City} & \textbf{No. of Vehicles} & \textbf{Total Cargo Delivered(Tons)}\\
\hline
New York, NY & Lusaka, Zambia & 266.7 & 40,005\\

New York, NY & Libreville, Gabon & 1,166.7 & 280,008\\

New York, NY & Luanda, Angola & 541.7 & 130,008\\

New York, NY & Dakar, Senegal & 208.3 & 49,992\\

Jacksonville, Florida & Lusaka, Zambia & 733.3 & 109,995\\

Jacksonville, Florida & Nairobi, Kenya & 1,133.3 & 169,995\\

Jacksonville, Florida & Khartoum, Sudan & 1,466.7 & 220,005\\

Khartoum, Sudan & Niamey, Niger & 666.7 & 100,005\\

Libreville, Gabon & Kosongo, D.R. Congo & 10,169.5 & 180,000\\

Nairobi, Kenya & Ndjamena, Chad & 333.3 & 49,995\\

Khartoum, Sudan & Ndjamena, Chad & 200.0 & 30,000\\
\hline
Total &  &  & 1,360,008\\


\end{tabular}
\end{table}
\pagebreak


## Case 3 - Maximum cargo flow 
Given tighter shipment restrictions on more routes, the network paths that maximizes total cargo dispatches only 816,170 tons cargo. Table 3 shows the  the routes used to achieve the maximum cargo,and the vehicle allocations for each of these routes. Unfortunately, in this case, only 6 destinations recieve its full cargo requirements. The 3 cities with lacking cargo are: Lusaka, Zambia; Kosongo, D.R. Congo; and Ndjamena, Chad. 

To increase the total cargo allocation, we can increase number of flights flown from Nairobi, Kenya and Khartoum, Sudan to Jacksonville, FL. We can increase number of flights by 60 and 80, respectively. These extra flights will cause bottlenecks for routes from Nairobi, Kenya and Khartoum, Sudan to Kosongo, D.R. Congo. The restriction on routes from Nairobi, Kenya and Khartoum, Sudan to Kosongo, D.R. Congo, should be increased by 60 and 80 respectively. These bottlenecks are largely driven by the cargo shortage in Kosongo, D.R. Congo, which is the largest.

```{r include=FALSE}
#include=FALSE
# Maximum Flow

# Set up model
mf <- make.lp(0, 41)
lp.control(mf, sense = "max")

## Set objective fn (Tons) =  (Tons/trip) x (trip), 
obj_fn <- c(rep(0, 32),rep(1, 9))
set.objfn(mf, obj_fn)

# Set up constraints
add.constraint(mf, c(1,1,rep(0, 39)),"<=", 1000000)
add.constraint(mf, c(-1,0,150,240,150,150,240,240,rep(0, 33)),"=",  0) #NY
add.constraint(mf, c(0,-1,0,0,0,0,0,0,150,240,150,150,240,240,rep(0,27)),"=",  0) #FL
add.constraint(mf, c(0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0,0,0),"=",  0) #Zambia
add.constraint(mf, c(0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0,0,0,0),"=",  0) #Gabon
add.constraint(mf, c(0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0),"=",  0) #Kenya
add.constraint(mf, c(0,0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0),"=",  0) #Sudan
add.constraint(mf, c(0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0),"=",  0) #Angola
add.constraint(mf, c(0,0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0),"=",  0) #Senegal
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),"=",  0) #Niger
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),"=",  0) #Congo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,1),"=",  0) #Chad
add.constraint(mf, c(rep(0, 32),-1,-1,-1,-1,-1,-1,-1,-1,-1), "<=", 1000000)

# Air Constraints
add.constraint(mf, c(0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 300*150) #NyZa
add.constraint(mf, c(0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 500*150) #NyKe
add.constraint(mf, c(0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 500*150) #NySu
add.constraint(mf, c(0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 500*150) #FlZa
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 700*150) #FlKe
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 600*150) #FlSu
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 200*150) #ZaNi
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 0) #KeNi
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 300*150) #SuNi
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 140*150) #ZaCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 40*150) #KeCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 80*150) #SuCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 0) #ZaCh
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 300*150) #KeCh
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,150,0,0,0,0,0,0,0,0,0,0,0),"<=", 40*150) #SuCh

# Truck Contraints
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 250*17.7) #AnCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0),"<=", 240*17.7) #AnCh
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0, 0,0,0,0,0,0,0,0,0),"<=", 300*17.7) #GaCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0, 0,0,0,0,0,0,0,0,0),"<=", 160*17.7) #GaCh
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),"<=", 700*17.7) #SeCo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17.7,0,0,0,0,0,0,0,0,0),"<=", 450*17.7) #Sech

# Aid Requirements Constraints
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),"<=", 150000) #Zambia
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),"<=", 100000) #Gabon
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),"<=", 120000) #Kenya
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0),"<=", 90000) #Sudan
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0),"<=", 130000) #Angola
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0),"<=", 50000) #Senegal
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),"<=", 100000) #Niger
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),"<=", 180000) #Congo
add.constraint(mf, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1),"<=", 80000) #Chad


dimnames(mf) <- list(c("Dummy Source","NY", "FL","Zambia", "Gabon", "Kenya",
                       "Sudan", "Angola", "Senegal", "Niger", "Congo", "Chad", "Dummy Sink",
                       "Ny-Zambia Air", "NY-Kenya Air", "NY-Sudan Air", "FL-Zambia Air", "FL-Kenya Air",
                       "FL-Sudan Air", "Zambia-Niger Air", "Kenya-Niger Air", "Sudan-Niger Air", "Zambia-Congo Air",
                       "Kenya-Congo Air", "Sudan-Congo Air", "Zambia-Chad Air", "Kenya-Chad Air", "Sudan-Chad Air",
                       "Angola-Congo Truck", "Angola-Chad Truck", "Gabon-Congo Truck", "Gabon-Chad Truck",
                       "Senegal-Congo Truck", "Senegal-Chad Truck",  "ZambiaD", "GabonD", "KenyaD", "SudanD", "AngolaD", "SenegalD", "NigerD", "CongoD", "ChadD"),
                       c("Du-NY", "Du-FL", "NY-ZM","NY-GA","NY-KE","NY-SU","NY-AN","NY-SE","FL-ZM","FL-GA","FL-KE","FL-SU","FL-AN","FL-SE","ZM-NI","GA-NI","KE-NI","SU-NI","AN-NI","SE-NI","ZM-CO","GA-CO","KE-CO","SU-CO","AN-CO","SE-CO","ZM-CH","GA-CH","KE-CH","SU-CH","AN-CH","SE-CH", "ZA-Du", "GA-Du", "KE-Du", "SU-Du", "AN-Du", "SE-Du", "NI-Du", "CO-Du", "CH-Du") )

# Solve the model
solve(mf)

# Make results and sensitivity table
ps <- get.primal.solution(mf)
obj_sa <- get.sensitivity.obj(mf)
rhs_sa <- get.sensitivity.rhs(mf)

nv <- length(get.variables(mf))
mc <- length(get.constr.type(mf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)],
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2))
colnames(sa_tab) <- c(rownames(mf), colnames(mf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")

# Objective value and sensitivity analysis table
ov
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30,  "inf",  sa_tab)
as.table(sa_tab)
```



\begin{table}
\caption{Recommended Allocation (Maximum Cargo Shipped)(For case 3)}
\centering
\begin{tabular}[t]{l l r r}
\hline
\textbf{Departure City} & \textbf{Arrival City} & \textbf{No. of Vehicles} & \textbf{Total Cargo Delivered(Tons)}\\
\hline
New York, NY & Lusaka, Zambia & 300.0 & 45,000 \\

New York, NY & Libreville, Gabon & 679.8 & 163,152 \\

New York, NY & Nairobi, Kenya & 500.0 & 75,000 \\

New York, NY & Khartoum, Sudan & 500.0 & 75,000 \\

New York, NY & Luanda, Angola & 577.8 & 138,672 \\

New York, NY & Dakar, Senegal & 293.1 & 70,344 \\

Jacksonville, Florida & Lusaka, Zambia & 500.0 & 75,000 \\

Jacksonville, Florida & Nairobi, Kenya & 640.0 & 96,000 \\

Jacksonville, Florida & Khartoum, Sudan & 520.0 & 78,000 \\

Libreville, Gabon & Niamey, Niger & 3107.3 & 54,999.21 \\

Khartoum, Sudan & Niamey, Niger & 300.0 & 45,000 \\

Libreville, Gabon & Kosongo, D.R. Congo & 300.0 & 5,310 \\

Nairobi, Kenya & Kosongo, D.R. Congo & 40.0 & 6,000 \\

Khartoum, Sudan & Kosongo, D.R. Congo & 80.0 & 12,000 \\

Luanda, Angola & Kosongo, D.R. Congo & 250.0 & 4,425 \\

Dakar, Senegal & Kosongo, D.R. Congo & 700.0 & 12,390 \\

Libreville, Gabon & Ndjamena, Chad & 160.0 & 2,832 \\

Nairobi, Kenya & Ndjamena, Chad & 300.0 & 45,000 \\

Khartoum, Sudan & Ndjamena, Chad & 40.0 & 6,000 \\

Luanda, Angola & Ndjamena, Chad & 240.0 & 4,248 \\

Dakar, Senegal & Ndjamena, Chad & 456.0 & 8,071.2\\
\hline
Total &  &  & 816,170\\

\end{tabular}
\end{table}
